\documentclass[10pt]{article}
\usepackage[a4paper, margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}

% Font settings
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}
\setlist[itemize]{noitemsep, topsep=0pt}

\begin{document}

% Header
\begin{center}
    {\huge Md Amanullah} \\
    Address: Eichendorffring 97, 35394 Germany \\
    \href{mailto:md.amanullah@mni.thm.de}{md.amanullah@mni.thm.de} | \href{https://www.linkedin.com/in/m-amanullah/}{LinkedIn: m-amanullah} | \href{https://github.com/amanullahmd}{GitHub: amanullahmd}
\end{center}

% Education
\section*{Education}
\textbf{University of Applied Sciences Mittelhessen (THM)}, Gießen, Germany \hfill \textit{04/2023 -- Present} \\
Bachelor of Science in Computer Science \\
\textbf{Concentration}: Full Stack Java Development, Cloud Computing \& DevOps, AI \\
\textbf{Related Coursework}: Data Structures and Algorithms, Object-Oriented Programming, Machine Learning, Cloud Computing, Web Development.

% Experience
\section*{Experience}

 \textbf{Aptiv}, Wuppertal, Germany \hfill \textit{IT and Network Support, 11/2021 - 03/2023} \\
 \begin{itemize}
    \item Installed and configured servers, switches, and routers; specialized in structured wiring and cable management.
    \item Maintained networks, replaced hardware, and handled optical gear and system configurations.
    \item Proficient in networking (TCP/IP, OSI, VLAN) and Red Hat Linux; managed client support via SAP ticketing system.\\
\end{itemize}

\textbf{University of Applied Sciences Mittelhessen (THM)}, Gießen, Germany \hfill \textit{Student Project, 2024} \\
\textit{Space Invaders Game - Java Edition} \\
\begin{itemize}
    \item Created a Java-based "Space Invaders" game using OOP and MVC architecture.
    \item Used Processing library for graphics, collision detection, and scoring.
    \item Integrated JUnit 5 for unit testing to ensure gameplay reliability.
\end{itemize}

% Projects
\section*{Projects}

\textbf{Spring CRUD Application}, \hfill \textit{2023-2024} \\
\begin{itemize}
    \item Developed a CRUD application using Spring Boot, Spring Data JPA, and MySQL for user management.
    \item API Endpoints: POST /user/add, GET /user, GET /user/get?id={id}, PUT /user/update?id={id}, DELETE /user/delete/{id}.
\end{itemize}

\textbf{Login Registration Server}, \hfill \textit{2023-2024} \\
\begin{itemize}
    \item Created a backend service for user registration and login with secure password handling using Spring Boot and H2.
\end{itemize}

\textbf{React Login Registration}, \hfill \textit{2023-2024} \\
\begin{itemize}
    \item Developed a React application for user registration and login with responsive design and error handling.
\end{itemize}

\textbf{Angular and Spring Boot E-commerce}, \hfill \textit{2023-2024} \\
\begin{itemize}
    \item Built a complete e-commerce application using Angular and Spring Boot.
\end{itemize}

\textbf{AWS Microservices with Spring Boot}, \hfill \textit{2023-2024} \\
\begin{itemize}
    \item Implemented microservices with Spring Boot, deployed on AWS for scalability.
\end{itemize}

% Skills
\section*{Skills}

\begin{tabbing}
    \textbf{Programming:} \= Java, JavaScript, Python, HTML/CSS, TypeScript, SQL, NoSQL, Node.js, Angular.js, React.js, \\ Next.js, C \\
    \textbf{Technical:} \> Spring Boot, Data Structures, AWS, Maven, Hibernate, JPA, Docker, Kubernetes, NMap, \\ DevOps, Bootstrap, Wireshark, MS-365 \\
    \textbf{Platforms:} \> Linux, Windows, MacOS \\
    \textbf{Languages:} \> German, English, Bangla, Hindi \\
    \textbf{Interests:} \> Cricket, Football, Video Games, Reading Books \\
\end{tabbing}

\end{document}
